Optimal management of a stochastically varying population when policy adjustment is costly

### 2015-01-20 manuscripts/manuscript.Rmd
finishing off edits from paul and mike

```{r Figure_1, fig.cap="Estimated stock abundances (top panels) show much greater variation than the corresponding harvest policies (bottom).  Left panels: ICCAT Stock assessments and Total Allowable Catch (TAC, before adjustments for national underages and overages) for bluefin tuna, 1982 - 2007. Right panels: SEDAR stock assessments and annual quotas for south Atlantic snowy grouper.", fig.width=6, fig.height=4, dev=c("pdf", "svg", "png"), cache=FALSE}
tuna <- read.csv("components/data/tuna.csv")
grouper <- read.csv("components/data/grouper.csv")

@@

To illustrate this tradeoff, we use an example from fisheries
management. Figure 1, top-left panel, shows a time series for the
estimated population size, represented as spawning stock biomass, of
west Atlantic bluefin tuna (_Thunnus thynnus_, henceforth bluefin) from
a recent stock assessment [@ICCAT2009a].  The bottom-left panel 
shows the catch quota (Total Allowable Catch or TAC, before being adjusted
for overages or underages in the catch of each country in the previous year)
for the stock as set by the relevant
management agency [@ICCAT2009a]. Despite the estimated population size
declining by `r 1 - min(tuna$stock)/max(tuna$stock)`% between 1982 and 1991, the quota was not changed during
this period. Instead, the quota only changed occasionally and in between
times was left unaltered. Fishery management decisions regarding this
species can be highly contentious (@Safina1998, @Sissenwine1998,
@Porch2005). Moreover, the stock is fished by fleets from many nations
with quotas being set by a multilaterial management agency through a
process of negotiation. As such, we might reasonably anticipate that
for this species there could be substantial transaction costs involved
in reaching agreement over any quota change, or constraints on the frequency
with which the those changes could occur.  Either could contribute to
the observed quota stability. Such patterns of variable stocks managed
under far less variable quotas are extremely common; for instance, 
in the management of south Atlantic snowy grouper (_Epinephelus niveatus_) 
shown in the right-hand panels [@SEDAR2013]. More generally, reviews by @Biais1995 and
@Patterson2007a document many cases where changes in catch
quotas that a management agency set were more modest than changes that
would be recommended just by considering variations in stock abundance.

@@

where $N_t$ the stock size, $h_t$ the harvested level, 
$Z_t$ gives the stochastic shocks, which we
assume are lognormally distributed and $A$ and $B$ are positive
constants.

@@

ggplot(fees, aes(c2, (npv0-value)/npv0, lty=variable, color=variable)) + 
  geom_line() + 
  geom_hline(aes(yintercept=reduction), linetype=4) + 
  xlab("Penalty coefficient") +
  ylab("Reduction in net present value") + 
  scale_linetype_discrete(labels=relabel, breaks = c('L1', 'L2', 'fixed')) + 
  scale_color_discrete(labels=relabel, breaks = c('L1', 'L2', 'fixed'))

@@

Figure 3 illustrates how the different forms of adjustment cost can
impact the dynamics of the optimal harvest policy. Corresponding stock
sizes can be seen in the supplement.  Each panel is generated against the
same sequence of environmental variability so that they can be compared
directly.  The harvest policy chosen shows a systematic deviations from
the adjustment cost free optimum, depending on the structure of the cost function.  In each
case, the optimal solution without any adjustment cost is shown with
the policy induced by optimization under the given cost structure 
(equivalent to a `r 100*reduction`% reduction in maximum expected NPV)
overlaid in blue.

@@

```{r Figure_4, fig.cap="Variance and autocorrelation of harvest dynamics, as a function of the penalty coefficient.  Adjustment penalty is calculated as percentage of the maximum expected $NPV$ in the basic case with no policy adjustment costs.", fig.height=4, fig.width=8, cache=fig.cache, dev=c("pdf", "svg", "png")}

@@

f4df <- filter(figure4_df, timeseries=='harvest')
ggplot(f4df, aes(penalty_fraction, value, fill=penalty_fn, col=penalty_fn)) + 
  stat_summary(fun.y = mean, 
               fun.ymin = function(x) mean(x) - sd(x), 
               fun.ymax = function(x) mean(x) + sd(x), 
               geom = "ribbon", alpha=0.3, colour=NA) +
  stat_summary(fun.y = mean, geom = "line") + 
  coord_cartesian(xlim = c(0, .3)) + 
  facet_wrap(~ statistic, scale="free_y") + 
  scale_color_discrete(labels=relabel, name="Penalty function") + 
  scale_fill_discrete(labels=relabel, name="Penalty function") +
  xlab("Penalty size (as fraction of NPV0)")

@@

While still not common for the particular parameter combinations we examine,
We find that positive unaltered quotas through time are much more likely
to occur when optimizing against $\Pi_1$ where policy adjustment costs
scale linearly with the size of proposed policy changes: over the 100 replicates
time series the harvest policy is strictly positive and identical in consecutive intervals
only `r no_shifts[["L2"]] * 100`% of the time for quadratic costs $\Pi_2$, compared with
`r no_shifts[["L1"]] * 100`% with linear costs $\Pi_1$ and `r no_shifts[["fixed"]]*100`%
for fixed costs $\Pi_3$. Moreover, these occurrences increase in frequency as the severity of
these costs ($c_i$) increases.

@@

Reed <- cbind(reed_profits, costs = reed_costs$V1, Assumption = "Reed") 
Adj <- cbind(profits, costs = costs$V1, Assumption = "Adjustment penalty")

@@

```{r}
fig5_caption <- paste("Distribution of profits from fishing and costs paid to adjustment, under linear costs ($\\Pi_1$). (Alternate penalties can be found in the supplementary materials)  Distributions are shown when managing a system in which the adjustment costs present compared to the same costs and profits of managing the system using a Reed model, which ignores adjustment costs, and thus tends to pay higher fees for adjustment.  In contrast, the difference in profit after accounting for costs is only marginally less than the value derived by managing the population to optimize profits when ignoring adjustment costs (Reed model).")
```

@@

Next we examine the consequences either of ignoring policy adjustment
costs when they are present or assuming they are present when they are
not. To do so, we run two kinds of simulations:

1. Simulations in which the optimal policy accounts for adjustment costs, 
   and those costs are present (in the form assumed),
2. Simulations in which the optimal policy _does not_ account for adjustment costs,

While the optimization ensures that on average, the policy in the first
simulation should outperform that of the second, it does not tell us by
how much.  These simulations thus allow us to quantify this effect.

We provide 100 replicates of each kind of scenario for each of the
three forms $\Pi_1$, $\Pi_2$ & $\Pi_3$.  For each, we record (a)
the dockside profits derived from fishing as well as (b) any fees paid
to make adjustments to the policy.  In the first kind of simulation,
dockside revenues are almost less than in the second for a given
stochastic replicate, since the latter optimizes the expected NPV.
However, the costs paid for adjustment are almost always less in the
first scenario as well, since this solution explicitly tries to avoid
higher adjustment costs.  We visualize this pattern in the distributions
shown in Figure 5 (focusing on $\Pi_1$ for simplicity, as the pattern
in $\Pi_2$ and $\Pi_3$ is similar, see Supplementary Material.)

Figure 5 shows that the difference in dockside revenue (labeled "profits"
in the figure) between these two scenarios (green vs purple distributions)
is very small, while a larger difference exists between the costs paid
for making policy adjustments (red vs blue). This is predicted by the
optimization: the first scenario must outperform (or at least equal)
the NPV of the second scenario in aggregate, and as it cannot do so
through higher profits it must do so through lower costs.  Interestingly,
for this set of parameters very little is lost in dockside revenue.
This suggests that the impact of assuming costs are present when they
are not is rather small: since the dockside revenue is none-the-less
near optimal.  This also suggests that the converse error: ignoring
costs when they are present, is more severe.

```{r Figure_6, fig.cap="Relative cost of ignoring adjustment costs when they are present ('ignoring', red) vs assuming the adjustment costs when they are absent ('assuming', blue), shown by penalty function over increasing magnitudes of cost.  All values are relative to the cost-free adjustment optimum, $NPV_0$.  In each case, it is less costly to assume adjustment costs are present when they are not than it is to ignore them when they are present. The severity of the latter mistake increases sharply as adjustment costs make a larger fraction of the total costs.", dev=c("pdf", "svg", "png"), fig.width=7, cache=FALSE}

@@

We visualize the differences between these two errors directly in Figure
6. Subtracting revenue from adjustment costs and considering only the mean
across the replicates, we can dervive the expected $NPV$ in each case.
To standardize against a common baseline, we will express this value as a
fraction of the cost-free optimum, $NPV_0$. Note that we have calibrated
the optimal solutions to anticipate that `r reduction*100`% of their
$NPV$ would go into adjustment costs. When these adjustment costs are
not actually present (blue bars, Fig 6), we thus expect a $NPV$ higher
than the anticipated `r (1 -reduction)*100`% but not quite as high as
the optimal policy for that scenario (100%).  When adjustment costs are
present but the policy assumes that they are not (red bars), we would
expect the $NPV$ to be less than `r (1 - reduction) * 100`% of $NPV_0$
(since that's as good as the optimal solution for this scenario can do).

@@

Policy-makers managing ecological systems that vary in space and time
must evaluate how much of that variation to reflect in management
recommendations. Fine-tuning a policy to respond to frequent variations
in ecological dynamics may incur increased transaction costs associated
with constantly revisiting past policy decisions. A more pragmatic
approach would be one that balances benefits from responding to frequent
variations in ecological conditions with the increased transaction costs
involved. As a first step towards exploring these ideas, we revisited
a classic problem from bioeconomics concerning the optimal management
of a fish stock subject to stochastically varying recruitment [@Reed1979; @Clark2010]. 
We examined how optimal policy recommendations, here
annual catch quotas, changed when accounting for costs associated with
policy adjustment and what the implications of following these policy
recommendations would be for the exploited population. We also compared
how the value of the fishery is affected by managers either under-
or over-estimating the importance of policy adjustment costs of this type.

Estimating policy adjustment costs and how they respond to the size of
proposed policy changes would be empirically challenging. Recognizing
this fact, we compared different plausible forms that
these costs might take. We compared two cost structures where we assumed
the magnitude of policy adjustment costs increased with the magnitude
of the change in policy being proposed with an alternative formulation
in which we assumed there was a fixed cost associated with making any
change to current policy. While each formulation clearly provides only a
very phenomenological representation of the policy setting environment,
we believe that each enables us to explore meaningful differences in how
policy adjustment costs might operate. That being said, in the real-world
we might expect the different types of adjustment cost to operate in
combination.

The biggest differences between the representations of policy adjustment
cost that we consider are between those that have a smoothing effect on
annual quotas and those that do not. The few past studies that incorporate
policy adjustment costs in models of fisheries or other environmental
management contexts [@Feichtinger1994; @Wirl1999] have assumed costs of
policy adjustment increased as a quadratic function of the magnitude of
the policy change being proposed (analogous to $\Pi_2$ formulation). In
effect, this means that small changes to annual quotas incur little
extra cost, but large changes to annual quotas become disproportionately
expensive to make. Including costs of this form smooths inter-annual
variation in the catch quotas that would be recommended. Also, the catches
and remaining stock sizes corresponding to optimal management become more
autocorrelated in time, because it takes the fishery longer to harvest
down peaks in abundance that follow large recruitment pulses. The effects
of smoothing here are similar to those predicted when assuming the cost
per unit effort is increasing in the amount of effort expended (e.g.,
@Lewis1981, @McGough2009; see Supporting Information for a summary of the
relevant results) as opposed to associating extra costs with changes to
policy *per se*. Smoothing effects of this type are what one might have
expected when including policy adjustment costs.

Standing in sharp contrast to these smoothing predictions is our
finding that including policy adjustment costs can actually _increase_ the
variability of quotas through time if there is a fixed cost associated
with making any changes to current policy (e.g. costs of running relevant
stakeholder meetings and public consultations on proposed policy changes,
$\Pi_3$). With this formulation, as stock sizes vary in response to
recruitment, the fishery manager must balance the cost of brokering
a policy change with the cost in forgone fisheries revenue from not
responding to favorable recruitment pulses. The optimal policy involves
ignoring small variations in recruitment, but then assigns a larger quota
when particularly strong recruitment years arise than would have been
the case in the absence of policy adjustment costs. The other functional
form we consider, in which the costs of policy adjustment scale linearly
with the size of the adjustment ($\Pi_1$), has less obvious effects on
optimal policies. But interestingly, it is the formulation that
most frequently produces stretches of strictly positive but unchanging
quotas of the type most commonly encountered in real-world applications.

That the different representations of policy adjustment costs result in
such different dynamics suggests that researchers constructing fisheries
economics models should proceed cautiously when choosing how to represent
these costs. However, in our own experience, we have found that while
modeling studies sometimes mention policy adjustment costs when motivating
model assumptions [e.g. @Feichtinger1994; @Wirl1999; @Lewis1981; @McGough2009], they rarely provide much justification
for the choice of functional form used or test the sensitivity of any
conclusions drawn to alternative specifications. Indeed, we were surprised
to find such clear differences between the functional forms, because
we anticipated that the limiting case of increasing policy adjustment
costs within each functional form should be the same, namely a constant
annual quota that does not change through time (open-loop control).

We also compared the efficiency costs that would result from failing
to account for policy adjustment cost if they are present with those
involved in assuming them when in fact they are absent. The results
of this comparison were not sensitive to the particular form of policy
adjustment costs assumed. Instead, we always found the efficiency costs
of ignoring policy adjustment costs when they were present to be much
larger than the efficiency costs of assuming policy adjustment costs
applied when they were in fact absent. Policy adjustment costs affect
the overall value of the fishery in two ways here. First, there is the
direct cost associated with each quota change. Second there is a cost in
foregone revenue from missed catches when not following what would be the
optimal policy if quotas were free to track recruitment variability. Our
finding that it is more costly to ignore policy adjustment costs when
they are present arises because the first, more direct, cost contribution
here is larger than the second.

@@

As with any modeling analysis, our formulation makes many assumptions. For
example, we assume that the fishery in question is being optimally managed
by a policy-maker who acts as the 'sole owner' of the stock. This approach
is different to models that assume fisheries are not well-managed,
e.g. by assuming open access conditions,
or ones that derive policy recommendations endogenously by modeling
interactions between different stakeholders [@Kaitala1993; @Laukkanen2003].
As such, we anticipate that our approach will be more relevant to
some fisheries, particularly domestic fisheries in developed countries
that are subject to relatively strong regulatory regimes, than to others
(e.g., artisanal fisheries that are subject to weaker regulation). To
focus on the effects of policy adjustment costs, we focused narrowly
on the basic model specification of @Reed1979 and examined how the
predictions of this classic problem were changed by introducing policy
adjustment costs of different forms. However, there have been many
elaborations on Reed's basic approach that increase the realism of
the optimization models involved by relaxing other assumptions (see for
example @Sethi2005; @Singh2006; @McGough2009).

One obvious research avenue suggested by our models is that of empirically
estimating costs of policy adjustment. A direct estimation approach
could quantify some sources of policy adjustment costs, e.g. costs to
processing plants that arise from having more variable catches. However,
other more intangible sources of policy adjustment costs, e.g. preferences
of policy-makers or different stakeholders for less variable quotas,
might be missed. An alternative, more holistic, approach would be to
apply revealed preference methods to fisheries management agencies
themselves, in the tradition of [@McFadden1975; @McFadden1976]. Such an analysis
would involve comparing quotas that were set relative to stock sizes as
they were estimated at the time each management decision was taken to
try to infer what objective managers were maximizing.

A worthwhile modeling extension suggested by our results would be to
examine the implications of policy adjustment costs for risks of stock
collapse. Examining risks of stock collapse is not possible with the
Reed model-formulation that we followed here but would be worthwhile
in light of our finding that the variance and autocorrelation in stock
sizes through time can be affected when accounting for costs of policy
adjustment. Both are properties known in other modeling settings to
be associated with changes to the risk of extinction or of transitions
between alternative stable states [@Scheffer2009]. This highlights the risk
that changes in management policies can either mimic or mask such possible
early warning signs of sudden transitions, and points to another way
in which more context is needed before such approaches can be useful to
management [@Boettiger2013].

When facing highly variable ecological systems, how often should
natural resource managers respond? A highly interventionist strategy
would track ecosystem variation very closely. Alternatively, a manager
might choose only to take action or change policy only when conditions
look very different to those previously experienced. We took a modeling
approach to begin to explore these ideas. Specifically, we focused on
a well-known problem from fisheries management and examined how optimal
management recommendations changed when we accounted for costs associated
with frequently changing management decisions. While we focused on a
fisheries context, our findings would be relevant to many other settings
where natural resource managers revisit management decisions through
time in light of ecological variability, including game management,
management of in-stream flow rates, fire management, habitat restoration,
and managing for endangered species. In some ways, the analyses that
we present can also be thought of as providing a temporal counter-part
to discussions about the optimal spatial scale over which ecosystem
management should be conducted.

>>>>

```{r Figure_1, fig.cap="Estimated stock abundances (top panels) show much greater variation than the corresponding harvest policies (bottom).  Left panels: ICCAT Stock assessments and Total Allowable Catch (TAC, before adjustments for national underages and overages) for bluefin tuna, 1982 - 2007. Right panels: SEDAR stock assessments and annual quotas for south Atlantic snowy grouper, 1994-2012.", fig.width=6, fig.height=4, dev=c("pdf", "svg", "png"), cache=FALSE}
tuna <- read.csv("components/data/tuna.csv")
grouper <- read.csv("components/data/grouper.csv")

@@

To illustrate this tradeoff, we use an example from fisheries
management. Figure 1, top-left panel, shows a time series for the
estimated population size, represented as spawning stock biomass, of
west Atlantic bluefin tuna (_Thunnus thynnus_, henceforth bluefin) from
a recent stock assessment [@ICCAT2009a].  The bottom-left panel 
shows the catch quota (Total Allowable Catch or TAC, before being adjusted
for overages or underages in the catch of each country in the previous year)
for the stock as set by the relevant
management agency [@ICCAT2009a]. Despite the estimated population size
declining by `r 1 - min(tuna$stock)/max(tuna$stock)`% between 1982 and 1991, the quota was not changed during
this period. Instead, the quota only changed occasionally and in between
times was left unaltered. Fishery management decisions regarding this
species can be highly contentious (@Safina1998, @Sissenwine1998,
@Porch2005). Moreover, the stock is fished by fleets from many nations
with quotas being set by a multilaterial management agency through a
process of negotiation. As such, we might reasonably anticipate that
for this species there could be substantial transaction costs involved
in reaching agreement over any quota change, or constraints on the frequency
with which the those changes could occur.  Either could contribute to
the observed quota stability.

Such patterns of variable stocks managed
under far less variable quotas are extremely common; for instance, 
in the management of south Atlantic snowy grouper (_Epinephelus niveatus_) 
shown in the righthand panels [@SEDAR2013]. Though the stock assessment
shows similarly frequent variation between 1994 and 2012, the quota has
only been adjusted twice during this period. In contrast to the adjustment
in the bluefin quotas, both adjustments in snowy grouper quotas were phased
in through steps over several years: 1994-96 and 2005-08.
More generally, reviews by @Biais1995 and
@Patterson2007a document many cases where changes in catch
quotas that a management agency set were more modest than changes that
would be recommended just by considering variations in stock abundance.

@@

where $N_t$ the stock size, $h_t$ the harvested level, 
$Z_t$ gives the stochastic shocks, which we
assume are log-normally distributed and $A$ and $B$ are positive
constants.

@@

ggplot(fees, aes(c2, (npv0-value)/npv0, lty=variable, color=variable)) + 
  geom_line() + 
  geom_hline(aes(yintercept=reduction), linetype=4) + 
  xlab("Penalty coefficient") +
  ylab("Reduction in net present value") + 
  scale_linetype_discrete(labels=relabel, breaks = c('L1', 'L2', 'fixed')) + 
  scale_color_discrete(labels=relabel, breaks = c('L1', 'L2', 'fixed')) 
 # rename scale from 'variable' to 'adjustment cost for policy:'

@@

Figure 3 illustrates how the different forms of adjustment cost can
impact the dynamics of the optimal harvest policy. Corresponding stock
sizes can be seen in the supplement.  Each panel is generated against the
same sequence of environmental variability so that they can be compared
directly.  The harvest policy chosen shows a systematic deviations from
the adjustment cost free optimum, depending on the structure of the cost function.  
In each case, the optimal solution without any adjustment cost is 
shown by the dashed grey line, with
the policy induced by optimization under the given cost structure 
(equivalent to a `r 100*reduction`% reduction in maximum expected NPV)
overlaid in solid blue.

@@

```{r Figure_4, fig.cap="Variance and autocorrelation of harvest dynamics, as a function of the penalty coefficient.  Adjustment penalty is calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=4, fig.width=8, cache=fig.cache, dev=c("pdf", "svg", "png")}

@@

f4df <- filter(figure4_df, timeseries=='harvest')
ggplot(f4df, aes(penalty_fraction, value, fill=penalty_fn, col=penalty_fn)) + 
  stat_summary(fun.y = mean, 
               fun.ymin = function(x) mean(x) - sd(x), 
               fun.ymax = function(x) mean(x) + sd(x), 
               geom = "ribbon", alpha=0.3, colour=NA) +
  stat_summary(fun.y = mean, geom = "line") + 
  coord_cartesian(xlim = c(0, .3)) + 
  facet_wrap(~ statistic, scale="free_y", ncol=1) + 
  scale_color_discrete(labels=relabel, name="Penalty function") + 
  scale_fill_discrete(labels=relabel, name="Penalty function") +
  xlab(paste0("Penalty size (as fraction of", expression(NPV[0]), ")"))

@@

While still not common for the particular parameter combinations we examine,
We find that positive unaltered quotas through time are much more likely
to occur when optimizing against $\Pi_1$ where policy adjustment costs
scale linearly with the size of proposed policy changes: over the 100 replicates
time series the harvest policy is strictly positive and identical in consecutive intervals
only `r no_shifts[["L2"]] * 100`% of the time for quadratic costs $\Pi_2$, compared with
`r no_shifts[["L1"]] * 100`% with linear costs $\Pi_1$ and `r no_shifts[["fixed"]]*100`%
for fixed costs $\Pi_3$. Moreover, these occurrences increase in frequency as the severity of
these costs ($c_i$) increases. Note that the restriction of only positive quotas lets us 
distinguish between cases that are constant due purely to adjustment costs from cases that
are constant purely due to boundary effects.

@@

Reed <- cbind(reed_profits, costs = reed_costs$V1, Assumption = "No adjustment penalty") 
Adj <- cbind(profits, costs = costs$V1, Assumption = "Adjustment penalty")

@@

```{r}
fig5_caption <- paste("Distribution of revenues from fishing and costs paid to adjustment. Plot shows distributions for the linear costs structure ($\\Pi_1$) only, alternate penalties can be found in the supplementary materials. Dockside revenues are always higher than adjustment costs.  When those costs are not accounted for in the policy ("no adjustment costs"), it is possible to obtain only marginally higher revenues, but pay higher adjustment costs.")
```

@@

<!-- this is confusing and could use better wording.  Consider naming the 
scenarios, e.g. omission error vs optimal-->

Next we examine the consequences either of ignoring policy adjustment
costs when they are present or assuming they are present when they are
not.

To do so, we will simulate managing a fish stock when adjustments are costly.
We will perform 100 replicate simulations of this for each of the three
cost structures, $\Pi_1$, $\Pi_2$, & $\Pi_3$.  For each replicate, we will
use two different management policies: one which ignores the adjustment costs,
(that is, the Reed optimum policy, $\Pi_0$), and a second which accounts for the
adjustment cost in place.

By comparing the NPV of this second scenario against the first, we can
quantify the impact of ignoring costs when they are present.

Figure 5 shows that the difference in dockside revenue (labeled "profits"
in the figure) between these two scenarios (green vs purple distributions)
is very small, while a larger difference exists between the costs paid
for making policy adjustments (red vs blue). This is predicted by the
optimization: the first scenario must outperform (or at least equal)
the NPV of the second scenario in aggregate, and as it cannot do so
through higher profits (these having already been maximized by the cost-free strategy),
it must do so through lower costs.  Interestingly,
for this set of parameters very little is lost in revenue.
This suggests that the impact of assuming costs are present when they
are not is rather small, as the revenue is nonetheless
near optimal.  This also suggests that the converse error -- ignoring
costs when they are present -- is more severe.

```{r Figure_6, fig.cap="Relative cost of ignoring adjustment costs when they are present ('ignoring', red) vs assuming the adjustment costs when they are absent ('assuming', blue), shown by penalty function over increasing magnitudes of cost.  All values are relative to the cost free adjustment optimum, $NPV_0$.  In each case, it is less costly to assume adjustment costs are present when they are not than it is to ignore them when they are present. The severity of the latter mistake increases sharply as adjustment costs make a larger fraction of the total costs.", dev=c("pdf", "svg", "png"), fig.width=7, cache=FALSE}

@@

<!-- This needs to be worded more clearly. At least the first 2 sentences here.  -->

We illustrate the differences between these two errors directly in Figure
6. Subtracting revenue from adjustment costs and considering only the mean
across the replicates, we can derive the expected $NPV$ in each case.
To standardize against a common baseline, we will express this value as a
fraction of the cost free optimum, $NPV_0$. Note that we have calibrated
the optimal solutions to anticipate that `r reduction*100`% of their
$NPV$ would go into adjustment costs. When these adjustment costs are
not actually present (blue bars, Fig 6), we thus expect a $NPV$ higher
than the anticipated `r (1 -reduction)*100`% but not quite as high as
the optimal policy for that scenario (100%).  When adjustment costs are
present but the policy assumes that they are not (red bars), we would
expect the $NPV$ to be less than `r (1 - reduction) * 100`% of $NPV_0$
(since that's as good as the optimal solution for this scenario can do).

@@

Policymakers managing ecological systems that vary in space and time
must evaluate how much of that variation to reflect in management
recommendations. Finer tuning a policy to respond to frequent variations
in ecological dynamics may incur increased transaction costs associated
with constantly revisiting past policy decisions. A more pragmatic
approach would be one that balances benefits from responding to frequent
variations in ecological conditions with the increased transaction costs
involved. As a first step towards exploring these ideas, we revisited
a classic problem from bioeconomics concerning the optimal management
of a fish stock subject to stochastically varying recruitment [@Reed1979; @Clark2010]. 
We examined how optimal policy recommendations -- here
annual catch quotas -- changed when accounting for costs associated with
policy adjustment and what the implications of following these policy
recommendations would be for the exploited population. We also compared
how the value of the fishery is affected by managers either under-
or overestimating the importance of policy adjustment costs of this type.

Estimating policy adjustment costs and how they respond to the size of
proposed policy changes would be empirically challenging. Recognizing
this fact, we compared different plausible forms that
these costs might take. We compared two cost structures where we assumed
the magnitude of policy adjustment costs increased with the magnitude
of the change in policy being proposed with an alternative formulation
in which we assumed there was a fixed cost associated with making any
change to current policy. While each formulation provides only
very phenomenological representations of the policy-setting environment,
we believe that each enables us to explore meaningful differences in how
policy adjustment costs might operate. That being said, in the real world
we might expect the different types of adjustment cost to operate in
combination.

The biggest differences between the representations of policy adjustment
cost that we consider are between those that have a smoothing effect on
annual quotas and those that do not. The few past studies that incorporate
policy adjustment costs in models of fisheries or other environmental
management contexts [@Feichtinger1994; @Wirl1999] have assumed costs of
policy adjustment increased as a quadratic function of the magnitude of
the policy change being proposed (analogous to $\Pi_2$ formulation). In
effect, this means that small changes to annual quotas incur little
extra cost, but large changes to annual quotas become disproportionately
expensive to make. Including costs of this form smooths inter-annual
variation in the recommended catch quotas. Also, the catches
and remaining stock sizes corresponding to optimal management become more
autocorrelated in time, because it takes the fishery multiple timesteps to harvest
down peaks in abundance that follow large recruitment pulses. The effects
of smoothing here are similar to those predicted when assuming the cost
per unit effort is increasing in the amount of effort expended (e.g.,
@Lewis1981, @McGough2009; see Supporting Information for a summary of the
relevant results) as opposed to associating extra costs with changes to
policy *per se*. Smoothing effects of this type are what one might have
expected when including policy adjustment costs.

Standing in sharp contrast to these smoothing predictions is our
finding that including policy adjustment costs can actually _increase_ the
variability of quotas through time if there is a fixed cost associated
with making any changes to current policy (e.g. costs of running relevant
stakeholder meetings and public consultations on proposed policy changes,
$\Pi_3$). With this formulation, as stock sizes vary in response to
recruitment, the fishery manager must balance the cost of brokering
a policy change with the cost in forgone fisheries revenue from not
responding to favorable recruitment pulses. The optimal policy involves
ignoring small variations in recruitment, but then assigns a larger quota
when particularly strong recruitment years arise than would have been
the case in the absence of policy adjustment costs. The other functional
form we consider, in which the costs of policy adjustment scale linearly
with the size of the adjustment ($\Pi_1$), has less obvious effects on
optimal policies. Interestingly, it is this structure that
most frequently produces stretches of strictly positive but unchanging
quotas of the type most commonly encountered in real world applications.

That the different representations of policy adjustment costs result in
such different dynamics suggests that researchers constructing fisheries
economics models should proceed cautiously when choosing how to represent
these costs. However, in our own experience, we have found that while
modeling studies sometimes mention policy adjustment costs when motivating
model assumptions [@Lewis1981; @Feichtinger1994; @Wirl1999; @McGough2009],
they rarely provide much justification
for the choice of functional form used or test the sensitivity of any
conclusions drawn to alternative specifications. Indeed, we were surprised
to find such clear differences between the functional forms, because
we anticipated that the limiting case of increasing policy adjustment
costs within each functional form should be the same, namely a constant
annual quota that does not change through time (open loop control).

We also compared the efficiency costs that would result from failing
to account for policy adjustment costs, if they are present, with those
involved in assuming them when in fact they are absent. The results
of this comparison were not sensitive to the particular form of policy
adjustment costs assumed. Instead, we always found the efficiency costs
of ignoring policy adjustment costs when they were present to be much
larger than the efficiency costs of assuming policy adjustment costs
applied when they were in fact absent. Policy adjustment costs affect
the overall value of the fishery in two ways here. First, there is the
direct cost associated with each quota change. Second there is a cost in
foregone revenue from missed catches when not following what would be the
optimal policy if quotas were free to track recruitment variability. Our
finding that it is more costly to ignore policy adjustment costs when
they are present arises because the first, more direct, cost contribution
here is the larger.

@@

As with any modeling analysis, our formulation makes many assumptions. For
example, we assume that the fishery in question is being optimally managed
by a policymaker who acts as the "sole owner" of the stock. This approach
is different to models that assume fisheries are not well managed,
e.g. by assuming open access conditions,
or models that derive policy recommendations endogenously by modeling
interactions between different stakeholders [@Kaitala1993; @Laukkanen2003].
As such, we anticipate that our approach will be more relevant to
some fisheries, particularly domestic fisheries in developed countries
that are subject to relatively strong regulatory regimes, than to others
(e.g., artisanal fisheries that are subject to weaker regulation). To
focus on the effects of policy adjustment costs, we focused narrowly
on the basic model specification of @Reed1979 and examined how the
predictions of this classic problem were changed by introducing policy
adjustment costs of different forms. However, there have been many
elaborations on Reed's basic approach that increase the realism of
the optimization models involved by relaxing other assumptions (see for
example @Sethi2005; @Singh2006; @McGough2009).

One obvious research avenue suggested by our models is that of empirically
estimating costs of policy adjustment. A direct estimation approach
could quantify some sources of policy adjustment costs, e.g. costs to
processing plants that arise from having more variable catches. However,
other more intangible sources of policy adjustment costs, e.g. preferences
of policymakers or different stakeholders for less variable quotas,
might be missed. An alternative, more holistic, approach would be to
apply revealed preference methods to fisheries management agencies
themselves, in the tradition of [@McFadden1975; @McFadden1976]. Such an analysis
would involve comparing quotas that were set relative to stock sizes as
they were estimated at the time each management decision was taken to
try to infer what objective managers were maximizing.

A worthwhile modeling extension suggested by our results would be to
examine the implications of policy adjustment costs for risks of stock
collapse. Examining risks of stock collapse is not possible with the
Reed model formulation that we followed here but would be worthwhile
in light of our finding that the variance and autocorrelation in stock
sizes through time can be affected when accounting for costs of policy
adjustment. Both are properties known in other modeling settings to
be associated with changes to the risk of extinction or of transitions
between alternative stable states [@Scheffer2009]. This highlights the risk
that changes in management policies can either mimic or mask such possible
early warning signs of sudden transitions, and points to another way
in which more context is needed before such approaches can be useful to
management [@Boettiger2013].

When facing highly variable ecological systems, how often should
natural resource managers respond? A highly interventionist strategy
would track ecosystem variation very closely. Alternatively, a manager
might choose only to take action or change policy only when conditions
look very different to those previously experienced. We took a modeling
approach to begin to explore these ideas. Specifically, we focused on
a well-known problem from fisheries management and examined how optimal
management recommendations changed when we accounted for costs associated
with frequently changing management decisions. While we focused on a
fisheries context, our findings would be relevant to many other settings
where natural resource managers revisit management decisions through
time in light of ecological variability, including game management,
management of instream flow rates, fire management, habitat restoration,
and managing for endangered species. The analyses that
we present can also be thought of as providing a temporal counterpart
to discussions about the spatial scale over which ecosystem
management.
